---
title: "R Notebook"
output: html_notebook
---

As per Michal's requset -- a short analysis on the influence of varying the establishment cost coefficient scale on the solution of the one depth cascade.

Load the information on the batch run that was used to examine the information

```{r}
library(tidyverse)
setwd("c:\\Users\\Adi Sarid\\Documents\\GitHub\\grid_robust_opt\\analysis\\Comparison - effect of establish coef on one-depth\\")
run_parameters <- readxl::read_excel("../16-08-2018-establish_cost_comparison.xlsx") %>%
  mutate(establish.cost = establish.cost*cost_coef_multiplier) %>%
  select(instance, establish.cost, upgrade.cost, dump_file)
  
```

Now we would like to examine the characteristics of the solutions. Do instances with a lower establishment cost, have more established edges that were not upgraded after establishment?

```{r}
all_files <- dir(pattern = "temp_sol.csv")

read_stamp <- function(file_name){
  tmp_res <- read_csv(file_name) %>%
    mutate(stamp = str_replace_all(file_name, ".0-temp_sol.csv", ""))
  return(tmp_res)
}

comparison_results <- map_df(.f = read_stamp, .x = all_files) 

optimality_gaps <- comparison_results %>%
  filter(name == "Opt. Gap.") %>%
  select(-name) %>%
  rename(opt_gap = value) %>%
  mutate(stamp = as.numeric(stamp))

comparison_clean <- comparison_results %>%
  mutate(stamp = as.numeric(stamp)) %>%
  filter(str_detect(name, "X|C|c")) %>%
  filter(str_detect(name, "_j")) %>% 
  mutate(var_type = case_when(str_detect(name, "X") ~ "X",
                              str_detect(name, "c") ~ "C")) %>%
  mutate(name = str_replace_all(name, "X_i|c|_i", "")) %>%
  separate(name, into = c("edge_i", "edge_j"), sep = fixed("_j")) %>%
  mutate(min_i = if_else(edge_i<edge_j, edge_i, edge_j),
         max_j = if_else(edge_i<edge_j, edge_j, edge_i)) %>%
  select(-edge_i,-edge_j) %>%
  mutate(edge_i = as.numeric(min_i),
         edge_j = as.numeric(max_j)) %>%
  select(-min_i, -max_j) %>%
  spread(var_type, value) %>%
  mutate(upgrade_type = case_when(is.na(X) & C == 1 ~ "Only upgrade",
                                  X == 1 & C == 0 ~ "Establish",
                                  X ==1 & C == 1 ~ "Establish and upgrade",
                                  TRUE ~ "No change")) %>%
  filter(upgrade_type != "No change") %>%
  left_join(run_parameters %>% select(dump_file, instance, establish.cost), 
            by = c("stamp" = "dump_file")) %>%
  left_join(optimality_gaps) %>%
  mutate(stamp = 
           paste0(instance, "-", stamp, "\n(cost=", establish.cost, "\ngap=", round(opt_gap, 2)*100,"%)")) %>%
  group_by(stamp) %>%
  count(upgrade_type)
  



ggplot(comparison_clean, aes(x = stamp, fill = upgrade_type, y=n)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  geom_label(aes(label = n), show.legend = FALSE, position = position_dodge(width = 1))
  


```